Evolution of Flare Activity in GKM Stars Younger than 300 Myr over Five Years of TESS Observations

### 2024-01-15 src/tex/ms.tex
newfits

\correspondingauthor{Adina~D.~Feinstein;\\ \twitter{afeinstein20}; \github{afeinstein20}} \email{adina.feinstein@lasp.colorado.edu}

@@

Miscellaneous figures and such that people might want but I don't need to show

@@

>>>>

@@

Here, we present all of our best-fit slopes and intercepts for various flare-frequency distributions (FFDs) fit throughout this work. We include our fits outlined in Sections~\ref{subsec:energy_ffd}. We present the FFDs as a function of energy in Figure~\ref{fig:simple_ffd_all}. We show 100 random draws from our MCMC fitting to these distributions as orange lines. We fit each distribution with $E > 10^{29}$\,erg, which roughly represents the turnover in each distribution. We do not fit the slope for $T_\textrm{eff} = [3850 - 4440]$~K at 20 -- 40~Myr due to our limited sample size (6 stars in total).

@@

\begin{deluxetable*}{l | r | r r r r r r }[!ht]
\tabletypesize{\footnotesize}
\tablecaption{Best-fit slope and normalization parameters for stars of different temperatures and ages\label{tab:best_fits}}
\tablehead{
\colhead{$T_\textrm{eff}$ [K]} & \colhead{Age [Myr]} & \colhead{$\alpha_\textrm{E}$} & \colhead{$\sigma_{\alpha_\textrm{E}}$} & \colhead{$\beta_\textrm{E}$} & \colhead{$\sigma_{\beta_\textrm{E}}$} &  \colhead{$n_\textrm{E, fit}$} & \colhead{$N_\textrm{E}$} %& \colhead{$\alpha_\textrm{T}$} & \colhead{$\sigma_{\alpha_\textrm{T}}$} & \colhead{$A_*$} & \colhead{$\sigma_{A_*}$} &  \colhead{$n_\textrm{T, tot}$} & \colhead{$n_\textrm{T, fit}$} & \colhead{$N_\textrm{T}$}
}
\startdata
2300 -- 3400 & 4 -- 10  &  -0.516  &  0.074  &  14.514  &  2.409  &  731  &  96 \\
& 10 -- 20  &  -0.336  &  0.031  &  8.296  &  0.973  &  1183  &  166 \\
& 20 -- 40  &  -0.499  &  0.058  &  13.564  &  1.858  &  526  &  75 \\
& 40 -- 50  &  -0.397  &  0.045  &  10.248  &  1.400  &  3358  &  111 \\
& 70 -- 80  &  -0.383  &  0.083  &  10.244  &  2.685  &  341  &  102 \\
& 120 -- 150  &  -0.657  &  0.097  &  18.757  &  3.161  &  3797  &  615 \\
& 150 -- 300  &  -0.341  &  0.063  &  8.799  &  2.029  &  295  &  60 \\
\hline
3400 -- 3850  & 4 -- 10  &  -0.206  &  0.025  &  4.536  &  0.821  &  397  &  44 \\
& 10 -- 20  &  -0.345  &  0.038  &  8.768  &  1.199  &  474  &  43 \\
& 20 -- 40  &  -0.405  &  0.054  &  10.890  &  1.741  &  194  &  17 \\
& 40 -- 50  &  -0.408  &  0.037  &  10.770  &  1.182  &  1420  &  43 \\
& 70 -- 80  &  -0.432  &  0.075  &  11.893  &  2.471  &  291  &  77 \\
& 120 -- 150  &  -0.525  &  0.062  &  14.557  &  1.998  &  1185  &  167 \\
& 150 -- 300  &  -0.339  &  0.058  &  8.683  &  1.904  &  262  &  56 \\
\hline
3850 -- 4440  & 4 -- 10  &  -0.221  &  0.040  &  4.884  &  1.314  &  207  &  34 \\
& 10 -- 20  &  -0.350  &  0.016  &  8.998  &  0.545  &  480  &  65 \\
& 20 -- 40  &  -0.202  &  0.077  &  4.425  &  2.492  &  51  &  6 \\
& 40 -- 50  &  -0.379  &  0.062  &  9.873  &  1.982  &  175  &  11 \\
& 70 -- 80  &  -0.455  &  0.102  &  12.498  &  3.347  &  63  &  25 \\
& 120 -- 150  &  -0.419  &  0.046  &  11.010  &  1.494  &  684  &  116 \\
& 150 -- 300  &  -0.323  &  0.029  &  8.026  &  0.929  &  247  &  39 \\
\hline
4440 -- 5270  & 4 -- 10  &  -0.348  &  0.031  &  8.850  &  1.014  &  112  &  25 \\
& 10 -- 20  &  -0.408  &  0.043  &  10.914  &  1.417  &  558  &  111 \\
& 20 -- 40  &  -0.440  &  0.033  &  11.635  &  1.075  &  250  &  29 \\
& 40 -- 50  &  -0.331  &  0.089  &  8.325  &  2.893  &  202  &  30 \\
& 70 -- 80  &  -0.390  &  0.085  &  10.152  &  2.749  &  122  &  37 \\
& 120 -- 150  &  -0.375  &  0.029  &  9.593  &  0.930  &  572  &  111 \\
& 150 -- 300  &  -0.560  &  0.126  &  15.056  &  3.951  &  115  &  35 \\
\hline
5270 -- 5930  &  4 -- 10  &  -0.271  &  0.049  &  6.280  &  1.586  &  166  &  44 \\
& 10 -- 20  &  -0.419  &  0.055  &  11.266  &  1.820  &  195  &  67 \\
& 20 -- 40  &  -0.465  &  0.035  &  12.377  &  1.149  &  636  &  58 \\
& 40 -- 50  &  -0.479  &  0.054  &  13.071  &  1.780  &  347  &  36 \\
& 70 -- 80  &  -0.337  &  0.083  &  8.416  &  2.656  &  57  &  27 \\
& 120 -- 150  &  -0.450  &  0.045  &  11.977  &  1.460  &  236  &  62 \\
& 150 -- 300  &  -0.305  &  0.081  &  6.826  &  2.598  &  64  &  22 \\
\enddata
\tablecomments{$n_\textrm{E, fit}$ is the number of flares fit per bin; $N_E$ is the number of stars in each bin.}
\end{deluxetable*}
